Pigeons.jl: Distributed sampling from intractable distributions

### 2024-05-22 paper/introduction.tex
Changes based on Trevor's comments

\medskip
Pigeons.jl\footnote{The source code for Pigeons.jl can be found at 
\url{https://github.com/Julia-Tempering/Pigeons.jl}. 
Pigeons.jl v0.2.0, used in the example scripts below, is currently compatible with Julia 1.8+.}
enables users to sample efficiently from high-dimensional and complex distributions 
and solve integration problems by 
implementing state-of-the-art sampling algorithms \cite{syed2021nrpt,surjanovic2022vpt} 
that leverage distributed computation. Its simple API allows users to perform such computations 
single-threaded, multi-threaded, and/or distributed over thousands of MPI-communicating 
machines. Further, it comes with guarantees on strong parallelism invariance wherein 
the output for a given seed is \emph{identical} irrespective 
of the number of threads or processes. 
Such a level of reproducibility is rare in distributed software but of 
great use for the purposes of debugging in the context of sampling algorithms, 
which produce stochastic output.
Specifically, Pigeons.jl is designed to be suitable and yield reproducible output for:
\begin{enumerate}
    \item one machine running on one thread;
    \item one machine running on several threads;
    \item several machines running, each using one thread, and
    \item several machines running, each using several threads.
\end{enumerate}

>>>>

\medskip
Pigeons.jl\footnote{The source code for Pigeons.jl can be found at 
\url{https://github.com/Julia-Tempering/Pigeons.jl}. 
Pigeons.jl v0.2.0, used in the example scripts below, is currently compatible with Julia 1.8+.}
enables users to sample efficiently from high-dimensional and complex distributions 
and solve integration problems by 
implementing state-of-the-art sampling algorithms \cite{syed2021nrpt,surjanovic2022vpt} 
that leverage distributed computation. Its simple API allows users to perform such computations 
single-threaded, multi-threaded, and/or distributed over MPI-communicating machines. 
We have stress-tested Pigeons successfully with up to 1000 machines running 
concurrently on a compute cluster (Sockeye) at the University of British Columbia.
Further, Pigeons comes with guarantees on strong parallelism invariance wherein 
the output for a given seed is \emph{identical} irrespective 
of the number of threads or processes. 
Such a level of reproducibility is rare in distributed software but of 
great use for the purposes of debugging in the context of sampling algorithms, 
which produce stochastic output.
Specifically, Pigeons.jl is designed to be suitable and yield reproducible output for:
\begin{enumerate}
    \item one machine running on one thread;
    \item one machine running on several threads;
    \item several machines running, each using one thread, and
    \item several machines running, each using several threads.
\end{enumerate}
